### 2018-04-10 paper/appendix.tex
parts edit for appendix

\section{Generating a Minimal CDD Expansion}
\label{app:cons-cdd}
% algorithm for constructing a CDD system:
\begin{algorithm}[t]
  % Declare IO markers.
  \SetKwInOut{Input}{Input}
  %
  \SetKwInOut{Output}{Output}
  % Declare sub-program (procedure) markers.
  \SetKwProg{myproc}{Procedure}{}{}
  % Inputs: a heap program and an error location.
  \Input{For $\mathcal{R} \in \relpreds$, %
    $\mathcal{S} \in \chc{\mathcal{R}}$.}
  % Output: inductive invariants.
  \Output{A minimal CDD expansion of $\mathcal{S}$ and
    correspondence to $\mathcal{S}$.} %
  \myproc{$\expand{ \mathcal{R} }(\mathcal{S})$ %
    \label{line:expand-begin} }{ %
    % auxiliary procedure:
    \myproc{$\expandaux( \mathcal{S}' )$
      \label{line:expand-aux-begin} }{ %
      % case split: optional sharing clause:
      \Switch{$\sharingclause( \mathcal{S}' )$}{ %
        % case: no siblings with overlapping descendants
        \lCase{$\none$:}{ \Return{$\mathcal{ S }'$} %
          \label{line:expand-ret} } %
        % case: siblings with 
        \lCase{$\mathcal{C} \in \mathcal{S}', % 
          R \in \ctxs{ \mathcal{R} }$: }{ %
          % expand the return:
          \Return{$\expandaux( %
            \copyrel{ \mathcal{R} }( %
            \mathcal{S}', \mathcal{C}, R))$ } %
          \label{line:expand-recurse}
        } %
      } %
    \label{line:expand-aux-end} } %
    % base call: 
    \Return{$( \expandaux(\mathcal{S}), \corr{ \mathcal{R} } )$ %
      \label{line:expand-base-call}}
  } %
  %
  \caption{$\expand{ \mathcal{R} }$: for $\mathcal{R} \in \relpreds$
    given $\mathcal{S} \in \chcs{ \mathcal{R} }$, returns a minimal
    CDD expansion of $\mathcal{S}$. }
  \label{alg:expand}
\end{algorithm}
% walk through top-level procedure:
\autoref{alg:expand}, given $\mathcal{S} \in \chcs{ \mathcal{R} }$
(\autoref{line:expand-begin}), returns an expansion $\mathcal{S}'$ of
$\mathcal{S}$ over relational predicates $\ctxs{ \mathcal{R} }$
(defined below) accompanied by a correspondence from $\mathcal{S}'$ to
$\mathcal{S}$.
%
$\expand{ \mathcal{R} }$ defines a procedure $\expandaux$
(\autoref{line:expand-aux-begin}---\autoref{line:expand-aux-end}) that
takes a CHC system $\mathcal{S}$ and returns an expansion of
$\mathcal{S}$.
%
$\expand{ \mathcal{R} }$ runs $\expandaux$ on $\mathcal{S}$ and
returns the result, paired with the map $\corr{ \mathcal{R} } : \ctxs{
  \mathcal{R} } \to \mathcal{R}$ (\autoref{line:expand-base-call};
$\corr{\mathcal{R}}$ is defined below).

% walk through aux procedure:
$\expandaux$, given $\mathcal{S}' \in \chcs{ \ctxs{ \mathcal{R} } }$,
runs a procedure $\sharingclause$ on $\mathcal{S}'$, which tries to
find $\mathcal{C} \in \mathcal{S}'$ and $R \in \ctxs{ \mathcal{R} }$
applied in the body of $\mathcal{C}$ that is a transitive dependences of
clause siblings in $\mathcal{S}'$.
%
I.e., $\expandaux$ tries to find $\mathcal{C}$ and $R$ such that for
some siblings $R_0, R_1 \in \ctxs{ \mathcal{R} }$, $R \in \depsof{
  \mathcal{S}' }(R_0) \intersection \depsof{ \mathcal{S}' }(R_1)$ and
$\relof{ \headof{ \mathcal{C} }} \in \depsof{ \mathcal{S}' }(R_0)
\setminus \depsof{ \mathcal{S}' }(R_1)$.
%
In such a case, we say that $(\mathcal{C}, R)$ is a
\emph{sibling-shared dependence}.
% case: no sibling-shares
If $\sharingclause$ determines that no sibling-shared dependence
exists, then $\expandaux$ returns $\mathcal{S}'$
(\autoref{line:expand-ret}).

% case: there is a sibling-shared dependence:
Otherwise, for sibling-shared dependence $(\mathcal{C}, R)$ returned
by $\sharingclause$, $\expandaux$ runs $\copyrel{ \mathcal{R} }$ on
$\mathcal{S}'$, $\mathcal{C}$, and $R$, which returns an expansion of
$\mathcal{S}'$ in which the dependents shared by $R_0$ and $R_1$ are
those shared in $\mathcal{S}'$, without $(\mathcal{C}, R)$.
%
$\expandaux$ recurses on the CHC system returned by $\copyrel{
  \mathcal{R} }$ and returns the result
(\autoref{line:expand-recurse}).

% give the representation of ctxs
\subsubsection{Representation of $\ctxs{ \mathcal{R} }$}
%
$\ctxs{ \mathcal{R} }$ are relational predicates that store the
clauses in which they occur.
%
\begin{defn}
  \label{defn:ctxs}
  $\ctxs{ \mathcal{R} }$ is the smallest space such that $\mathcal{R}
  \subseteq \ctxs{ \mathcal{R} }$ and for $\mathcal{C} \in \clauses{
    \mathcal{ \ctxs{R} } }$ and $A \in \appsof{ \bodyof{ \mathcal{C} }
  }$, $(\mathcal{C}, \relof{A}) \in \ctxs{ \mathcal{R} }$.
\end{defn}
% give the correspondence between relational predicates:
$\corr{ \mathcal{R} } : \ctxs{R} \to \mathcal{R}$ is such that for $R
\in \mathcal{R}$, $\corr{ \mathcal{R} }(R) = R$ and for $\mathcal{C}
\in \clauses{ \ctxs{R} }$ and $R \in \ctxs{R}$ such that
$(\mathcal{C}, R) \in \ctxs{R}$, $\corr{\mathcal{R}}(\mathcal{C}, R) =
\corr{ \mathcal{R} }(R)$.

% give the function that copies instances of a relational predicate
\subsubsection{Implementation of $\copyrel{ \mathcal{R} }$}
%
$\copyrel{\mathcal{R}}$, given $\mathcal{S} \in \chcs{ \mathcal{R} }$,
$\mathcal{C} \in \mathcal{S}$, and $R \in \ctxs{ \mathcal{R} }$,
returns the following CHC system.
% clause: C, but the application now points to (C, A)
Let $\mathcal{C}' \in \clauses{ \ctxs{ \mathcal{R} } }$ be
$\mathcal{C}$, with $R$ replaced with $(\mathcal{C}, R)$ in the body
of $\mathcal{C}$.
%
Let $\mathcal{S}_{ \mathcal{C} } \subseteq \clauses{ \ctxs{
    \mathcal{R} } }$ be the clauses in $\mathcal{S}$ for which $R$ is
the relational predicate of the clause head, and let
$\mathcal{S}_{\mathcal{C}}'$ be each clause in $\mathcal{S}_{
  \mathcal{C} }$, with $R$ in the clause head replaced with
$(\mathcal{C}, R)$.
%
Then $\copyrel{ \mathcal{R} }$ returns $\add{ (\remove{ \mathcal{S} }{
    \add{ \mathcal{S}_{\mathcal{C}} }{\mathcal{C} } }) }{ \mathcal{C}'
} \union \mathcal{S}_{\mathcal{C}}'$.
%

>>>>

\section{Generating a Minimal CDD Expansion}
\label{app:cons-cdd}
% algorithm for constructing a CDD system:
\begin{algorithm}[t]
  % Declare IO markers.
  \SetKwInOut{Input}{Input}
  %
  \SetKwInOut{Output}{Output}
  % Declare sub-program (procedure) markers.
  \SetKwProg{myproc}{Procedure}{}{}
  % Inputs: a heap program and an error location.
  \Input{A recruions-free CHC system $S$.}
  % Output: inductive invariants.
  \Output{A minimal CDD expansion $S'$ of $S$ and
    correspondence from $S'$ to $S$.} %
  \myproc{$\expand(S)$ %
    \label{line:expand-begin} }{ %
    % auxiliary procedure:
    \myproc{$\expandaux(S')$
      \label{line:expand-aux-begin} }{ %
      % case split: optional sharing clause:
      \Switch{$\sharingclause(S')$}{ %
        % case: no siblings with overlapping descendants
        \lCase{$\none$:}{ \Return{$S'$} %
          \label{line:expand-ret} } %
        % case: siblings with 
        \lCase{$C \in S', % 
          P \in \predof{S'}$: }{ %
          % expand the return:
          \Return{$\expandaux( %
            \copyrel(S', C, P))$ } %
          \label{line:expand-recurse}
        } %
      } %
    \label{line:expand-aux-end} } %
    % base call: 
    \Return{$( \expandaux(S), \corr )$ %
      \label{line:expand-base-call}}
  } %
  %
  \caption{$\expand$:
    given a recursion-free CHC system $S$, returns a minimal
    CDD expansion $S'$ of $S$ and its correspondence.}
  \label{alg:expand}
\end{algorithm}
% walk through top-level procedure:
\autoref{alg:expand}, given a recruion-free CHC system $S$
(\autoref{line:expand-begin}), returns an minimal CDD expansion $S'$ of
$S$ with a correspondence from $S'$ to
$S$.
%
$\expand$ defines a procedure $\expandaux$
(\autoref{line:expand-aux-begin}---\autoref{line:expand-aux-end}) that
takes a CHC system $S$ and returns an minimal CDD expansion of 
$S$.
%
$\expand$ runs $\expandaux$ on $S$ and
returns the result, paired with the map $\corr: \predof{S'} \to \predof{S}$ 
(\autoref{line:expand-base-call}).

% walk through aux procedure:
$\expandaux$, given a recursion-free CHC system $S'$,
runs a procedure $\sharingclause$ on $S'$, which tries to
find clause $C \in S'$ and predicate $P \in \bodyof{C}$
that $P$ is in both transitive dependences of two predicates $Q_0$ and $Q_1$ are siblings 
in $\predof{S}'$.
%
In such a case, we say that $(C, P)$ is a
\emph{sibling-shared dependence}.

% case: no sibling-shares
If $\sharingclause$ determines that no sibling-shared dependence
exists, then $\expandaux$ returns $S'$
(\autoref{line:expand-ret}).

% case: there is a sibling-shared dependence:
Otherwise, for sibling-shared dependence $(C, P)$ returned
by $\sharingclause$, $\expandaux$ runs $\copyrel $ on
$S'$, $C$, and $P$, which returns an expansion of
$S'$ by creates fresh copy $P'$ of $P$ and updates $\bodyof{C}$ 
to avoid transitive dependents shared by $Q_0$ and $Q_1$.
%
$\expandaux$ recurses on the CHC system returned by $\copyrel $ and returns the result
(\autoref{line:expand-recurse}).
%

### 2018-04-10 paper/approach.tex
parts edit for appendix

% talk about linear system
\begin{thm}
	\label{thm:cdd-contains}
  The class of CDD systems strictly contains the union of the classes
  of body-disjoint and linear systems.
\end{thm}
%
The CHC system $\mcchc$ (\autoref{sec:solve-ex}) is not body-disjoint
or linear, but is CDD.
%
A proof that both the classes of body-disjoint and linear systems are
contained in the class of CDD systems is given in \autoref{app:char}.

@@

% introduce solveCDD
the procedure $\solvecdd$ (\autoref{alg:solve-cdd}) is a solver for CDD systems.
%

$\solvecdd$, given a CDD system $\cc{S}$, it first do a topological sort on all
uninterpreted predicates in $\cc{S}$ based on their dependency relations.
%
In the order of topological sort, for each uninterpreted predicates $\cc{P}$ 
 $\solvecdd$ calles $\solveitp$ to compute the binary interpolation of 
 encoded pre and post formulas with the current solution.
 %
 If the conjunction of pre and post formulas is satisifiable, then $\solvecdd$
 returns $\nosoln$ to indicate this CDD system $\cc{S}$ is not solvable.
 %
 Otherwise, $\solvecdd$ binds the uninterpreted predicate $\cc{P}$ to the
 interpolation result $\cc{I}$ as part of the soltuion.
 %
 The encoding procedure $\prectr$ and $\postctr$ are defined below.
 %
 $\solvecdd$ returns the soltuion $\sigma$.

%
\begin{ex}
  $\solvecdd$, given $\mcchc$, may generate
  interpretations of $\mcpreds$ in any topological ordering of the
  dependency relation of $\mcchc$.
  %
  One such ordering is \cc{L4}, \cc{L6}, \cc{L8}, 
   \cc{L9}, \cc{db} and \cc{main}.
\end{ex}

>>>>

% talk about linear system
\begin{thm}
	\label{thm:cdd-contains}
  The class of CDD systems strictly contains the union of the classes
  of body-disjoint and linear systems.
\end{thm}
%
The proof is given in \autoref{app:char}.

@@

% introduce solveCDD
the procedure $\solvecdd$ (\autoref{alg:solve-cdd}) is a solver for CDD systems.
%
$\solvecdd$, given a CDD system $\cc{S}$, it first do a topological sort on all
uninterpreted predicates in $\cc{S}$ based on their dependency relations.
%
In the order of topological sort, for each uninterpreted predicates $\cc{P}$ 
 $\solvecdd$ calles $\solveitp$ to compute the binary interpolation of 
 encoded pre and post formulas with the current solution.
 %
 If the conjunction of pre and post formulas is satisifiable, then $\solvecdd$
 returns $\nosoln$ to indicate this CDD system $\cc{S}$ is not solvable.
 %
 Otherwise, $\solvecdd$ binds the uninterpreted predicate $\cc{P}$ to the
 interpolation result $\cc{I}$ as part of the soltuion.
 %
 The encoding procedure $\prectr$ and $\postctr$ are defined below.
 %
 $\solvecdd$ returns the soltuion $\sigma$.

%
\begin{ex}
  $\solvecdd$, given a CDD system $\mcchc$ in \autoref{sec:running-ex}, may generate
  interpretations queries in any topological ordering of the
  dependency relation of $\mcchc$.
  %
  One such ordering is \cc{L4}, \cc{L6}, \cc{L8}, 
   \cc{L9}, \cc{db} and \cc{main}.
\end{ex}

### 2018-04-10 paper/background.tex
parts edit for appendix

\subsubsection{Structure}
% definition of CHC
A Constrained Horn Clause contains a body and a head.
%
A body consisting of a conjunctive set of uninterpreted relational predicates applied to varialbes and a formula
that over variables.
%
A head can either be an uninterpreted relational predicates applied to variables or \cc{False}.
%
A Clause where the head is \cc{False} is called query.
\begin{defn}
  A Constrained Horn Clause is definied as follows: \\
  $\cc{chc} \Coloneqq \cc{head} \gets \cc{body}$ \\
  $\cc{head} \Coloneqq \cc{False} \mid \cc{pred}$  \\
  $\cc{body} \Coloneqq \varphi \wedge \cc{preds}$ \\
  $\cc{preds} \Coloneqq \cc{True} \mid \cc{pred} \wedge \cc{preds}$ \\
  $\cc{pred} \Coloneqq$ an uninterpreted predicate applied to variables \\
  $\varphi \Coloneqq$ a formula that all variables are vocabulary \\
\end{defn}
%
% define a body function, head function, and recursion-free
For a given constrained horn clause $C$, $\bodyof{C}$ denotes
the vector of uninterpreted predicates in the body of $C$, $\consof{C}$
denotes the formula in the body.
%
It is possible for a uninterpreted predicate shows multiple times in the
body of $C$.
%
For a given constrained horn clause $C$ that is not a query,
$\headof{c}$ denotes the uninterpreted predicates of the head of $C$.
%

@@

% define system of CHC's
We will present \sys as a solver for recursion-free CHCs.
%
For a given CHC system $\cc{S}$, there is no uninterpreted predicates $\cc{P} \in \predof{S}$ 
such that $\cc{P} \in \tdepsof{P}$, then $\cc{S}$ is a recursion-free CHCs system.

%
A solution to a CHC system $S$ is an interpretation of each
uninterpreted predicate $\cc{Q} \in \predof{S}$ that each clause holds
after substitute all predicates by its interpretation.

>>>>

\subsubsection{Structure}
% definition of CHC
A Constrained Horn Clause contains a body and a head.
%
A body consisting of a conjunction of a formula that over variables and a vector of uninterpreted predicates applied to varialbes.
%
A head can either be an uninterpreted predicates applied to variables or \cc{False}.
%
A Clause where the head is \cc{False} is called query.
\QZ{make it looks nice}
\begin{defn}
  A Constrained Horn Clause is definied as follows: \\
  $\cc{chc} \Coloneqq \cc{head} \gets \cc{body}$ \\
  $\cc{head} \Coloneqq \cc{False} \mid \cc{pred}$  \\
  $\cc{body} \Coloneqq \varphi \wedge \cc{preds}$ \\
  $\cc{preds} \Coloneqq \cc{True} \mid \cc{pred} \wedge \cc{preds}$ \\
  $\cc{pred} \Coloneqq$ an uninterpreted predicate applied to variables \\
  $\varphi \Coloneqq$ a formula that all variables are vocabulary \\
\end{defn}
%
% define a body function, head function, and recursion-free
For a given constrained horn clause $C$, $\bodyof{C}$ denotes
the vector of uninterpreted predicates in the body of $C$, $\consof{C}$
denotes the formula in the body.
%
It is possible for a uninterpreted predicate shows multiple times in the
body of $C$.
%
For a given constrained horn clause $C$ that is not a query,
$\headof{c}$ denotes the uninterpreted predicates of the head of $C$.
%

@@

%
For a given CHC system $\cc{S}$, there is no uninterpreted predicates $\cc{P} \in \predof{S}$ 
such that $\cc{P} \in \tdepsof{P}$, then $\cc{S}$ is a \emph{recursion-free} CHCs system.
%

%
A solution to a CHC system $S$ is a map that maps each each
uninterpreted predicate $\cc{P} \in \predof{S}$ to its interpretation which is a formula.
%
All clauses in $S$ holds
after substitute all uninterpreted predicates by its interpretation.
